---
title: "Statistical Concepts"
author: "Rithika Rao Dodda"
---

```{r}
# Load the file
random_variable <- readRDS("Causal_Data_Science_Data/random_vars.rds")
# Creating a Data Frame
df=data.frame(random_variable)
```

1. For each variable, Compute the following
```{r}
# 1.Mean 
mean(df$age)
mean(df$income)
```

```{r}
# 2. Variance
var(df$age)
var(df$income)
```

```{r}
# 3. Standard deviation
sd(df$age)
sd(df$income)
```

2. The estimated Standard deviations are on wide range of scales. Because of this, comparing them makes no sense.

3. Calculate Covariance and Correlation

```{r}
# Covariance
cov(df)
```

```{r}
# Correlation
cor(df)
```

4.  Correlation is easy to interpret as it is a standardized measure. When age is increasing the income is also increasing as the correlation is a positive value.

5. Compute the Conditional Expected value
```{r}
# 1
age_18 <- subset(df, age<=18, select = c(age,income))
mean(age_18$income)
```

```{r}
# 2
age_65 <- subset(df, age>=65, select = c(age,income))
mean(age_65$income)
```

```{r}
# 3
age_18_65 <- subset(df, age>=18 & age<65, select = c(age,income))
mean(age_18_65$income)
```
