---
title: "Regression and Statistical Inference"
author: "Rithika Rao Dodda"
---

# Assignmnet

```{r}
library(tidyverse)
```
```{r}
car_data <- readRDS("Causal_Data_Science_Data/car_prices.rds")
df_1=data.frame(car_data)
```
```{r}
# 1
dim(df_1)
```
There are 181 rows and 22 columns in the data file.

2. Using appropriate commands to get a more detailed look at the data.

```{r}
head(df_1)
```
```{r}
glimpse(df_1)
```
```{r}
summary(df_1)
```
The data types present are character and numeric data type.

3. Linear regression
```{r}
lm_all_factors <- lm(price ~ ., data = df_1)
summary(lm_all_factors)
```
All factors with a p-value less than 0.05 are relevant for the pricing of a car like carwidth, enginetypeohc, enginetypeohcv and enginesize  so on.

4. Choosing one regressor
```{r}
lm_one <- lm(price ~ enginesize, data = df_1)
summary(lm_one)
```

4.1 The regressor used was enginesize and it belongs to the numeric variables (discrete/continous).

4.2 As our estimate is positive (170.064), we have a positive effect. As a result increasing the enginesize would increase price of the car.

4.3 Yes, it  is satistically significant as the p value is lower than the significance level (0.05).

5. Add a variable seat_heating to the data
```{r}
df_1 %>% mutate(seatheating = TRUE)
```
```{r}
# Changing the variables from logical variables to numerical variables
df_2<- df_1 %>% mutate(seatheating = 1)
df_2
```
```{r}
# New regression
lm_new_variable <- lm(price ~ seatheating , data = df_2)
summary(lm_new_variable)
```
There is no relation between seat heating and pricing as there is no coefficient present in the new regression. If there is False value there might be coefficient value.


