---
title: "Directed Acyclic Graphs"
author: "Rithika Rao Dodda"
number-sections: false
---

# Assignment

```{r}
# Load necessary Libraries
library(tidyverse)
library(dagitty)
library(ggdag)
```

1. DAG for Parking Spots
```{r}
Parkingspots <- dagify(
  ParkingSpots ~ Location,
  Sales ~ Location,
  Sales ~ ParkingSpots,
  coords = list(x = c(Sales = 3, Location = 2, ParkingSpots = 1),
                y = c(Sales = 0, Location = 1, ParkingSpots = 0))
)
# Plot DAG
ggdag(Parkingspots, use_labels = "name", text =  F) + theme_dag()
```

When the store is located within the city, no parking spots are required because customers approach the store directly and do not need to arrange their visit. As a result, the sales depend on the location. However when the store is located outside of the city, parking spots are required which I believe has a direct impact on sales.

2. Regression
```{r}
# Load the file
car_prices <- readRDS("Causal_Data_Science_Data/customer_sat.rds")
# Create a Data Frame
df1=data.frame(car_prices)
```

2.1 Regress satisfaction on follow_ups 
```{r}
#lm_sf is the regresssion of satisfaction on follow_ups
lm_sf <- lm(satisfaction ~ follow_ups , data = df1)
summary(lm_sf)
```

2.2 Regress satisfaction on follow_ups and account for subscription
```{r}
#lm_sfa is the regresssion of satisfaction on follow_ups and account for subscription
lm_sfa <- lm(satisfaction ~ follow_ups + subscription , data = df1)
summary(lm_sfa)
```


3. Comparing the coefficients: 

In the first case, satisfaction on follow_ups are negatively correlated which suggests that the increase in satisfaction with the product and service will decrease the follow_up calls to the clients.

In the second case, satisfaction on follow_ups which accounts for subscription is highly correlated premium subscription levels than elite subscription levels.

4 Plot the data
```{r}
# Not conditioning on subscription
subscription_not_cond <- ggplot(df1, aes(x = satisfaction, y = follow_ups)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F)

# Conditioning on subscription 
subscription_cond <- ggplot(df1, aes(x = satisfaction, y = follow_ups, color = subscription)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F) +
  theme(legend.position = "right")

# Plot both plots
subscription_not_cond
subscription_cond
```

